---
title: "hw3"
author: "Jiajian Huang"
date: "4/6/2019"
output: html_document
---

```{r setup, include=FALSE}
library(ISLR)
library(glmnet)
library(fields)
library(rgl)
library(readbitmap)
library(imager)
library(readr)
library(pander); library(mice); library(Epi)
library(gridExtra); library(vcd); library(Hmisc)
library(mosaic); library(forcats); library(tidyverse)
library(OpenImageR)
library(class)
```

# Q8  CHP 9

## a.

```{r}
library(caret)
set.seed(2019)
train = sample(dim(OJ)[1], 800)
OJ.train = OJ[train, ]
OJ.test = OJ[-train, ]
```

## b.

```{r}
library(e1071)
svm.linear <- svm(Purchase ~ ., data = OJ.train, kernel = "linear", cost = 0.01)
summary(svm.linear)
```

From the output of R’s summary function we can see that 441 observations are used as support vector. Moreover, the support vectors are almost equally split among the classes.

## c.

```{r}
train.pred <- predict(svm.linear, OJ.train)
table(OJ.train$Purchase, train.pred)
```

```{r}
(80 + 55)/ ( 447+80+55+218)
```

The training error rate is 0.1688.

```{r}
test.pred <- predict(svm.linear, OJ.test)
table(OJ.test$Purchase, test.pred)
```

```{r}
(26+16)/(135+16+26+93)
```

The testing error rate is 0.1556.

## d.

```{r}
set.seed(2019)
tune.out = tune(svm, Purchase ~ ., data = OJ.train, kernel = "linear", ranges = list(cost = 10^seq(-2, 
    1, by = 0.25)))
summary(tune.out)
```

Tuning shows that optimal cost is 3.162278.

## e.

```{r}
svm.linear <- svm(Purchase ~ ., kernel = "linear", data = OJ.train, cost = tune.out$best.parameter$cost)
train.pred <- predict(svm.linear, OJ.train)
table(OJ.train$Purchase, train.pred)
```

```{r}
(75+61)/(441 + 61+ 75+223)
```

The training error rate is now 17%

```{r}
test.pred <- predict(svm.linear, OJ.test)
table(OJ.test$Purchase, test.pred)
```

```{r}
(25+16)/(135+25+16+94)
```

The test error rate is 15.18%.

## f.

```{r}
svm.radial <- svm(Purchase ~ ., kernel = "radial", data = OJ.train)
summary(svm.radial)
```

```{r}
train.pred <- predict(svm.radial, OJ.train)
table(OJ.train$Purchase, train.pred)
```

```{r}
(31+18)/(133+18+31+88)
```


```{r}
test.pred <- predict(svm.radial, OJ.test)
table(OJ.test$Purchase, test.pred)
```


```{r}
(80+37)/(465+37+80+218)
```

The classifier has a training error of 14.63% and a test error of 18.15%.

```{r}
set.seed(2019)
tune.out <- tune(svm, Purchase ~ ., data = OJ.train, kernel = "radial", ranges = list(cost = 10^seq(-2, 
    1, by = 0.25)))
summary(tune.out)
```

Tuning shows that optimal cost is 0.17.

## g.

```{r}
svm.poly <- svm(Purchase ~ ., kernel = "polynomial", data = OJ.train, degree = 2)
summary(svm.poly)
```

```{r}
train.pred <- predict(svm.poly, OJ.train)
table(OJ.train$Purchase, train.pred)
```

```{r}
(109+32)/(470+32+109+189)
```

```{r}
test.pred <- predict(svm.poly, OJ.test)
table(OJ.test$Purchase, test.pred)
```

```{r}
(41+17)/(134+17+41+78)
```

With polynomial kernel degree=2, the classifier has a training error of 17.63% and a test error of 21.48%.

```{r}
set.seed(2019)
tune.out <- tune(svm, Purchase ~ ., data = OJ.train, kernel = "polynomial", degree = 2, ranges = list(cost = 10^seq(-2, 
    1, by = 0.25)))
summary(tune.out)
```

Tuning shows that optimal cost is 0.17.

```{r}
svm.poly <- svm(Purchase ~ ., kernel = "polynomial", degree = 2, data = OJ.train, cost = tune.out$best.parameter$cost)
summary(svm.poly)
```

```{r}
train.pred <- predict(svm.poly, OJ.train)
table(OJ.train$Purchase, train.pred)
```

```{r}
(79+36)/(466+36+79+219)
```

```{r}
test.pred <- predict(svm.poly, OJ.test)
table(OJ.test$Purchase, test.pred)
```

```{r}
(33+20)/(131+20+33+86)
```

The classifier has a training error of 14.38% and a test error of 19.63%.

## h.

The default gamma approach provides the best results on this data.

# Dataset Khan

## random forests

```{r}
data("Khan")
```

```{r}
library(randomForest)
```

```{r}
dim(Khan$xtrain)
```

```{r}
dim(Khan$xtest)
```

```{r}
table(Khan$ytrain)
```

```{r}
table(Khan$ytest)
```


```{r}
khan_train = data.frame(x = Khan$xtrain, y = as.factor(Khan$ytrain))
khan_test = data.frame(x = Khan$xtest, y = as.factor(Khan$ytest))
```

```{r}
random = train(y ~ ., data = khan_train, method = "rf", trControl = trainControl(method = "cv"))
```


```{r}
confusionMatrix(khan_train$y, predict(random, khan_train))
```

```{r}
confusionMatrix(khan_test$y, predict(random, khan_test))
```

## tree boosting

```{r}
library(xgboost)
library(gbm)
```

```{r}
set.seed(2019)
boost.khan = gbm(y ~., data = khan_train, distribution = "gaussian", n.trees = 5000)
boost.khan
```

```{r}
par(mfcol = c(2, 4), mar = c(2, 2, 1, 1), las = 1)
plot(khan_train$y, predict(boost.khan, n.trees = 5000))
plot(khan_train$y, predict(boost.khan, n.trees = 5000) - khan_train$y, ylim = c(-20, 15));abline(h = 0)
```

```{r}
plot(khan_test$y, predict(boost.khan, khan_test, n.tree = 500))
plot(khan_test$y, predict(boost.khan, khan_test, n.trees = 500) - khan_test$y, ylim = c(-20, 15));abline(h = 0)
```

```{r}
set.seed(2019)
boost.han = gbm(y ~., data = khan_train, distribution = "gaussian", n.trees = 5000, interaction.depth = 4)
```

```{r}
yhat.bt1.nn = predict(boost.khan, khan_test, n.trees = seq(500, 5000, 500))
dim(yhat.bt1.nn)
```

```{r}
a = apply(yhat.bt1.nn, 2, function(x) mean(Khan$ytest - x)^2)
round(a, 5)
```

```{r}
boost.x = xgboost(data = Khan$xtrain, label = Khan$ytrain, max_depth = 4, eta = 1, nround = 5, objective = "reg:linear")
```

```{r}
all.equal(as.numeric(predict(boost.x, Khan$xtest) > 0.5), Khan$ytest)
```

```{r}
boost.y = xgboost(data = Khan$xtrain, label = Khan$ytrain, max_depth = 1, eta = 0.1, nround = 50, objective = "reg:linear")
```

```{r}
importance_matrix = xgb.importance(model = boost.x)
xgb.plot.importance(importance_matrix = importance_matrix)
```

```{r}
xgb.plot.importance(importance_matrix = xgb.importance(model =boost.y))
```








